Empty Homes V1

### 2017-06-26 LowUseEngland.Rmd
Fixing some bugs
there were all kinds of wied going on ... I think this has fixed it.

@@

@@

Hull

>>>>

CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.)

@@

(218977.5-  184071.4 )/184071.4

@@

#Hull
```{r}

Hull <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)

PlotMap(Hull, AG, variable = "WardLowUsePerc")

corplotter(Hull, "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Hull",
           "Low Use Percentage by Ward",
           "Median Price")

 HullStrap<-  DistribCompareBootstrapper(Hull, 1652, 1000)

 HullStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

HullStrap <- ValueTtest(HullStrap)

### 2017-06-26 LowUseLondon.Rmd
Fixing some bugs
there were all kinds of wied going on ... I think this has fixed it.

@@

Hull <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)

PlotMap(Hull, AG, variable = "WardLowUsePerc")

corplotter(Hull, "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Hull",
           "Low Use Percentage by Ward",
           "Median Price")
```

>>>>

 1762724.8-  426694.1

   test <- chelstrap %>% 
    select(class,ID, Homes, LowUse, HomesValue, LowUseValue) %>%
    group_by(ID, class) %>%
    summarise_all(funs(sum)) %>%
    mutate(HomesPrice = HomesValue/Homes,
           LowUsePrice = LowUseValue/LowUse)

ggplot(test, aes(x= class, y = LowUsePrice, fill = class)) + geom_boxplot()
 ggplot(test, aes(x= class, y = HomesPrice, fill = class)) + geom_boxplot()

  ggplot(test, aes(x= log(LowUsePrice), y = log(HomesPrice), colour = class)) + geom_point()  
```

@@

LambethStrap<-  Lambethinfo %>% filter(LAD11CD == "E09000022") %>% 
  DistribCompareBootstrapper(., 1652, 100)

LambethStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

#Why are lambteths results junk?
LamStrap <- ValueTtest(LambethStrap)

df <- LambethStrap

CamdenStrap<-  DistribCompareBootstrapper(Camdeninfo, 1652, 1000)

CamdenStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

#Why are lambteths results junk?
Camttest<- ValueTtest(CamdenStrap)

PlotMap(Camdeninfo,AG)
